Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-04 intro.tex
tweak some words in Introduction

Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
These works explore the possible job placement and routing configurations that could optimize the overall network performance without scrutinizing the possible interference.
In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
Our analysis focus on the performance of each application with interference in presence.

@@

We choose three representative applications from the DOE Design Forward Project~\cite{designforwardwebpage} to analyze the interference among them. Our study is based on the simulation with CODES, an high-fidelity, packet-level HPC network simulation toolkit~\cite{codes}.
For each application, we examine it with two job placement policies and three routing policies.
We make the following interesting observations through extensive simulation.

@@

    \item Random placement can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation.

    \item Contiguous placement can guarantee consistency performance of less communication-intensive applications by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.

@@

Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity. Thus, we propose a hybrid job placement, which can assign the communication-intensive applications with random allocation and less intensive applications with contiguous allocation. Our experiment results show that hybrid job placement can mitigate the performance degradation of less communication-intensive applications while still guarantee the best performance of communication-intensive applications.
%\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported so far. We believe the observations and new placement policy presented in this paper are valuable to the HPC community.
%We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators. 
%For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks. System software developers could design better scheduling algorithms for jobs with distinct communication behavior. System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.

The rest of this paper is organized as follows. Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies. Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project. Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations. Section \ref{sec:workload-2} validates the observations we obtain from previous section. Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network. Section \ref{sec:related work} discusses the related work. Finally, the conclusion is presented in Section \ref{sec:conclusion}.

>>>>

Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
These works explore the possible job placement and routing configurations that could optimize the overall network performance without scrutinizing the possible interference.
In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
Our analysis focus on the performance of every single application in the presence of interference .

@@

We choose three representative applications from the DOE Design Forward Project~\cite{designforwardwebpage} to analyze the interference among them. Our study is based on the simulation with CODES, an high-fidelity, packet-level HPC network simulation toolkit~\cite{codes}.
For each application, we examine it with two job placement policies and three routing policies.
We make the following interesting observations through extensive simulations.

@@

    \item Random placement can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation to the less intensive applications.

    \item Contiguous placement can guarantee the consistency performance of less communication-intensive applications by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.

@@

Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity. Thus, we propose a hybrid job placement, which assigns random allocations to the communication-intensive applications and contiguous allocations to the less intensive ones. Our experiment results show that hybrid job placement can mitigate the performance degradation for the less communication-intensive applications without affecting the performance of communication-intensive applications.
%\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported so far. We believe the observations and new placement policy presented in this paper are valuable to the HPC community.
%We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators. 
%For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks. System software developers could design better scheduling algorithms for jobs with distinct communication behavior. System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.

The rest of this paper is organized as follows. Section~\ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies. Section~\ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project. Section~\ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations. Section~\ref{sec:workload-2} validates the observations we obtain from previous section. Section~\ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network. Section~\ref{sec:related work} discusses the related work. Finally, the conclusion is presented in Section~\ref{sec:conclusion}.
